Dependent Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-13 main.tex
The second abstract

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\begin{document}
%
\title{Dependent Typed Multi-Stage Calculus\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Akira Kawata\inst{1} \and
Atsushi Igarashi\inst{2}\orcidID{0000-0002-5143-9764}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Graduate School of Informatics, Kyoto University, Kyoto, Japan\\
\email{akira@fos.kuis.kyoto-u.ac.jp} \and
\email{igarashi@kuis.kyoto-u.ac.jp}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
We develop yet another typed multi-stage calculus $\lambda^{\textrm{MD}}$.
It extends Hanada and Igarashi's $\lambda^{\triangleright\%}$ with dependent type.

@@

The first point is CSP in kinding rules.
$\lambda^{\TW\%}$ contains kinding rules because dependent types need them.

The second point is CSP in equivalence rules.

The abstract should briefly summarize the contents of the paper in 150--250 words.
\keywords{Multistage programming \and Dependent type \and Specification verification by tests.}
\end{abstract}
%
%
%
\section{First Section}
\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{color}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\begin{document}
%
\title{Dependent Typed Multi-Stage Calculus\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Akira Kawata\inst{1} \and
Atsushi Igarashi\inst{2}\orcidID{0000-0002-5143-9764}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Graduate School of Informatics, Kyoto University, Kyoto, Japan\\
\email{akira@fos.kuis.kyoto-u.ac.jp} \and
\email{igarashi@kuis.kyoto-u.ac.jp}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}

We develop yet another typed multi-stage calculus $\lambda^{\textrm{MD}}$.
It extends Hanada and Igarashi's $\lambda^{\triangleright\%}$ with dependent type.

@@

The first point is CSP in kinding rules.
$\lambda^{\TW\%}$ includes kinding rules because dependent types need them
but the relationship between kinds and stages was't clear.

The second point is CSP in equivalence rules.
Prameters of dependent types may contain cross-staed terms.
We give reasonable equivalence rules to handle them.

\keywords{Multistage programming \and Dependent type \and Specification verification by tests.}
\end{abstract}

\blue{203 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
%
%
%
\section{First Section}
\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.
